### 2010-12-03 report/report.tex
Edited RunManager description.
Added link.

\edit{write this}

@@

\item \code{RunManager} class \edit{write this}

@@

We stop each run after plateauing results (no improvement 
for one third of the policies seen so far)  (WHY??)

>>>>

A video presentation of this project should be viewed at http://www.youtube.com/watch?v=ODoiOj9DdGg.
\edit{write this}

@@

\item \code{RunManager} class: Deals with all the details of running the robot,
  including choosing an initial parameter, running the robot multiple times, 
  tracking distance walked, and writing to the log file. Also includes the
  \code{explore\_dimensions} method.

@@

The metric for evaluation of the designed gait is speed. A comparison and evaluation. We stop each run after plateauing results (no improvement 
for one third of the policies seen so far)  (WHY??)
